IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks

### 2016-07-05 ms_infocus.tex
Minor edits to improve outline.

@@

Yet Sazatornil \textit{et al.} do not include unobserved interactions in their quantifications of mismatches, so the test of the mismatch hypothesis actually includes also forbidden links effects: a full mismatch of corolla tube/proboscis lengths actually meaning a forbidden link.

>>>>

% Explain the biological basis of mismatch using Fig 1 and Arditti

@@

% Further synth of Sazatronil et al paper
% Forbidden links background.

Yet Sazatornil \textit{et al.} did not include the morphological difference for parameter estimation when interactions were not recorded. Thus the test of the mismatch hypothesis implicitly includes forbidden links effects: a full mismatch of corolla tube/proboscis lengths actually means a forbidden link. In any case the mismatch hypothesis somehow captures the fact that a fraction of the unobserved interactions in these hawkmoth/flower assemblages is due to extreme phenotypic mismatch (i.e., size-related forbidden links).

Proper tests of coevolutionary hypotheses in hawkmoth/flower assemblages (and plant-animal mutualisms in general) should use Sazatornil et al. approach: assessing match/mismatch patterns for every possible pairwise interaction among partners within complex webs of interaction where multiple life-history attributes may contribute biological reasons to expect forbidden links.
